NumPy---Array Computation for Python

### 2019-12-20 body.tex
Add figure to illustrate broadcasting

The \emph{universal functions} (or \emph{ufuncs})
are functions written in C that implement efficient looping over
NumPy arrays. An important feature of ufuncs is the built-in
implementation of \emph{broadcasting}.  For example, the function
\code{arctan2(x, y)} is a ufunc that accepts two arguments and computes
$\tan^{-1}(y/x)$.  The ufunc loops over the dimensions of the inputs
in such a way that if, say, \code{x} is a 1-d array with length 3, and
\code{y} is a 2-d array with shape $2 \times 1$, the output will be
an array with shape $2 \times 3$.  The ufunc machinery takes care
of calling the function with all the appropriate combinations of
input array elements to compute the output array.
The elementary arithmetic operations of addition, multiplication, etc.,
are implemented as ufuncs, so broadcasting applies even in expressions
such as \code{x + y * z}.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth]{static/broadcasting}
  \caption{
    Broadcasting a $1 \times 3$ array against a $2 \times 1$ array
    yields a $2 \times 3$ result.
  }
  \label{fig:broadcasting}
\end{figure}

The \emph{universal functions} (or \emph{ufuncs})
are functions written in C that implement efficient looping over
NumPy arrays. An important feature of ufuncs is the built-in
implementation of \emph{broadcasting}.  For example, the function
\code{arctan2(x, y)} is a ufunc that accepts two arguments and computes
$\tan^{-1}(y/x)$.  The ufunc loops over the dimensions of the inputs
in such a way that if, say, \code{x} is a 1-d array with length 3, and
\code{y} is a 2-d array with shape $2 \times 1$, the output will be
an array with shape $2 \times 3$ (see Figure~\ref{fig:broadcasting}).  The ufunc machinery takes care
of calling the function with all the appropriate combinations of
input array elements to compute the output array.
The elementary arithmetic operations of addition, multiplication, etc.,
are implemented as ufuncs, so broadcasting applies even in expressions
such as \code{x + y * z}.
